\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\author{Justin Zhu}
\title{Self-Reliance in the Digital Age}
\begin{document}
\maketitle

The society that Emerson writes about in his Self-Reliance work is one ingrained in fundamental principles of nature. How come?  What is the natural world that Emerson writes about?

Every Mac Desktop and Windows PC comes with a default desktop background of a natural landscape.  The world of the 21st century is completely digital, and human interaction may be part of a bygone era.  Is this a falsehood that governs our day-to-day activities or is this something more fundamental?

The idea that Emerson has contrived is one where true work is independent with the other notions of identity. 

In 'Self-Reliance', Emerson discusses the fundamental
importance of asserting the individual self, comprising of
several steps such as speaking your latent conviction, and
the like.  What is this conviction?

\section{Emerson's weaknesses and addressing these weaknesses}

Is nature if ideas inspire them?  Are those ideas legitimate?  What makes us say that these ideas are part of what we want to do or say?


\section{Privileges}
Broadly speaki

Emerson writes that, "But do your work, and I shall know you. Do your work, and you shall reinforce yourself."  But what is this work that Emerson talks about?
  
In an ideal world, everybody is able to find meaning in the
work that they do, deriving meaning from this work.
We often think about professors, CEOs, and these sorts of
individuals who are very much privileged people in the top
echelon of society, but rarely do we consider the other
half, that is, the people who are not at all positioned to think about their own lives.

However, only a certain number of people have the ability to
work towards making this work a reality, and that itself is
the infeasibility, the impossibility of Emerson's goals.

How can we best reconcile what Emerson is speaking?  How
Emerson is saying it?  It is very much our own personal
biases, judgments shrouding our ability to speak upon such
matters, and that itself is often unsatisfactory.  To
understand these large philisophical studies and 

\section{Digital Self-Reliance}

The notion of identity has become one that is intertwined with other aspects of other identity.  This identity is one that is not solely divorced from other notions of what is right or wrong.  The virtues that Emerson writes about is largely independent with that of other virtues.  Chiefly speaking, our ideas on the world and how we are to mold it into our very own creation can be seen to be tangentially related to what we describe as the optimal virtue, a world where our efforts are largely independent with that of other students.

\section{Meaningful Work in the Realm of Computational Thinking}
The computers where we think about meaningful work is often ill-contrived.  Not many people are well-maintained. 

In ``Deep Work," Newport writes about how his work is entrenched in basic principles.


\section{Nietzsche}

Romantic quest has the genius vs. them the crowd, the others.

Celestial body.  Stendhal's Red and Black is Christian because it involves the fall.  You read books, that's why you find yourself more compatible.  Then you fall in love.  Several things must happen.  There is definitely a falling away, falling from the natural habits according to your class standing, education, et cetera.  Stories that are Biblical to their core.

How that rebellion takes place, the possibility of imminent critique.  It's not until late 60's.  There is another version of this, an idealistic person comes with a simple realization in the end.  Understand the way things are run.

\section{Bound}

Spirited, Rational, Appetitive

Harmonic Development

Privatized Sublime

For Plato, his Republic is all the judgment plains.  If he can approach every situation he is in.  
\end{document}